Selection Coefficients

### 2021-09-02 graphs_newt_snakes/selection_coefficients.Rmd
added some more plots aand wrote some explinaation. I also added more to no space slim to make an interaction rate

```{r, making resueable figures}

@@

var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE){

@@

   if(just_two==TRUE){
     just2 <- cbind(data_frame_newt_x, data_frame_snake_y)
     just2 <- just2[-4]
       p <- ggplot(just2) +
    #xlim(0, 1000)+
      ggtitle(title, subtitle = subt) +
      xlab(x_label) + ylab(y_label)+
      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y)), color = "darkgreen", alpha=0.1)+
      theme(plot.title = element_text(size=5)) +
      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
  }
  if(logy==TRUE){
    p = p + scale_y_log10()
  }
  return(p)

}
```

@@

@@

>>>>

```{r, making resueable figures, results='hide', message=FALSE, warning=FALSE}

@@

var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE, colored=FALSE, color_label=NULL, highcol="darkseagreen"){

@@

   if(just_two==TRUE){
     just2 <- cbind(data_frame_newt_x, data_frame_snake_y)
     just2 <- just2[-4]
       p <- ggplot(just2) +
    #xlim(0, 1000)+
      ggtitle(title, subtitle = subt) +
      xlab(x_label) + ylab(y_label)+
      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y)), color = "darkgreen", alpha=0.1)+
      theme(plot.title = element_text(size=5)) +
      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
   }

   if(colored==TRUE){
     color3 <- cbind(data_frame_newt_x, data_frame_snake_y, data_frame_newt_y)
     color3 <- color3[-c(1,3,4,6)]
     suppressWarnings(suppressMessages(suppressPackageStartupMessages({require(scales)})))
     amin <- 0.1
     lowcol.hex <- as.hexmode(round(col2rgb(highcol) * amin + 255 * (1 - amin)))
     lowcol <- paste0("#",   sep = "",
                 paste(format(lowcol.hex, width = 2), collapse = ""))
       p <- ggplot(color3) +
    #xlim(0, 1000)+
      ggtitle(title, subtitle = subt) +
      xlab(x_label) + ylab(y_label)+
      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y), color = value_y.1))+
      theme(plot.title = element_text(size=5)) +
      scale_colour_gradient(high = highcol, low = lowcol) + 
      labs(colour = color_label) +
      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
  }
  if(logy==TRUE){
    p = p + scale_y_log10()
  }

  return(p)

}

@@

Sinse there seems to be an interaction between phenotype and population size, I will look at how the population size lines up with the mean phenotype of newts and snakes. I predict that there will be an arc of color ranging from light to dark depending on which species has a higher population size.

```{r, popsize of newts and snakes with color of phenotype}
vc1 <- var_by_var(Newt_pop_size, Newt_mean_Pheno, Newt_mean_Pheno, Snake_pop_size, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred")

vc2 <- var_by_var(Newt_pop_size, Snake_mean_Pheno, Snake_mean_Pheno, Snake_pop_size, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue")

vc1 
vc2
# for(i in 1:107){
# print(i)
# Newt_mean_Pheno_1 <- making_data_frames(files[i], all_of("Newt_mean_Pheno"))
# Snake_mean_Pheno_1 <- making_data_frames(files[i], all_of("Snake_mean_Pheno"))
# Newt_pop_size_1 <- making_data_frames(files[i], all_of("Newt_pop_size"))
# Snake_pop_size_1 <- making_data_frames(files[i], all_of("Snake_pop_size"))
# 
# naame_of_file= paste0("~/Desktop/figs/both_", i, ".png")
# png(filename =naame_of_file)
# vc_11 <- var_by_var(Newt_pop_size_1, Newt_mean_Pheno_1, Newt_mean_Pheno_1, Snake_pop_size_1, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred")
# #dev.off()
# 
# #naame_of_file_2= paste0("~/Desktop/figs/snakes_", i, ".png")
# #png(filename = naame_of_file_2)
# vc_12 <- var_by_var(Newt_pop_size_1, Snake_mean_Pheno_1, Snake_mean_Pheno_1, Snake_pop_size_1, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue") 
# print(grid.arrange(vc_11, vc_12))
# dev.off()
#}
```

I made some nice whale graphs! When the newt population size is large and the snakes population size is small the newt phenotype is high. When the newt population size is small and the snake population size is large the newts have a lower phenotype. Something strange happens with the phenotype of the snake, it is higher when the newt population size is large and the snake population size is small. The snake phenotype is also high when the snake population size is large and the newt population size is small. My theory is that the few remaining snakes in an area of very toxic newts are very resistant, but why don't we see the opposite happening in newts? <- this also happens in the snake-newt papers weird.
I would be wary of the whale graphs because these are a combined results of 107 simulations with a sample collected every 20 generations. It might be different in each separate simulation.

@@

Now, I am just going to run some numbers to see what the interaction rate was in my 1on1 slim simulation and what is should be set to in my nospace slim. In my 1on1 slimulations I us an interaction rate of 0.05 and surprisingly when I reverse calculate it from the mean number of interactions and mean population size I get 0.05 so it seems like it is working which is good (population specific to snake pop size).

```{r, relationship of interaction and pop size}

population_size = 700
number_of_interaction = 40

interaction_rate = number_of_interaction/population_size

print(paste0("If the population size is ", population_size, " and the number of interactions is ", number_of_interaction, ", then the interation rate is ", interaction_rate, "."))

population_size = 600
number_of_interaction = 40
interaction_rate = number_of_interaction/population_size

print(paste0("If the population size is ", population_size, " and the number of interactions is ", number_of_interaction, ", then the interation rate is ", interaction_rate, "."))

population_size = 800
number_of_interaction = 40
interaction_rate = number_of_interaction/population_size

print(paste0("If the population size is ", population_size, " and the number of interactions is ", number_of_interaction, ", then the interation rate is ", interaction_rate, "."))

interaction_rate = 0.05
population_size = 700
number_of_interaction = population_size*interaction_rate
print(paste0("Now if I pick the interaction rate of ", interaction_rate, " and the number of individuals is ", population_size, ", the number of interactions should be ", number_of_interaction))

var_by_var(newt_pop_size, newt_found, newt_found, snake_pop_size, title="Newt VS Snake Population Size Color = Number of Interaction", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Population Size", x_label="Newt Population Size", colored=TRUE, color_label="Interaction")

This light green cloud shows that when the population size is larger there are more interactions. This picture reminds me of a rain cloud.

It seems like using the formula population_size*interaction_rate will get me the correct number of interactions every time so I should devise a way to have a normal distribution with a mean around 40.
